---
title: "PHD_Clustering_Submission"
author: "Sanjyot Godbole"
date: "May 10, 2019"
output: html_document
---

```{r setup, include=FALSE}
# clear your environment
rm(list = ls(all=TRUE))
```

# Problem Description

* To  segment the customers which will help to understand their sensitivity to the interest rate or product features to improve retention ie., to reduce the default or transfer of loan to competition and to understand how to structure offers for better revenue.

# Reading & Understanding the Data

```{r}
fullDataDF = read.csv('finalDF.csv', header = T)
```

# Data Pre-processing

*Deleting the columns which are not required for further analyis 
* Deleting 47 columns 

```{r}

fullDataDF$Salary_binned_kmeans = NULL
fullDataDF$Salary_binned = NULL
fullDataDF$ageYears_binned_kmeans = NULL
fullDataDF$ageYears_binned = NULL
fullDataDF$credRScore_binned_kmeans = NULL
fullDataDF$credRScore_binned = NULL
fullDataDF$Starting_Instalment = NULL
fullDataDF$Maturity_Period = NULL
fullDataDF$Starting_outstanding = NULL
fullDataDF$Current_Instalment_Sequence = NULL
fullDataDF$Current_Outstanding = NULL
fullDataDF$UtilitySpending_binned_kmeans = NULL
fullDataDF$UtilitySpending_binned = NULL
fullDataDF$Total_no_of_loan_tenure_with_current_binned_kmeans = NULL
fullDataDF$Total_no_of_loan_tenure_with_current_binned = NULL
fullDataDF$Avg_loan_paid_in_transaction_binned_kmeans = NULL
fullDataDF$Avg_loan_paid_in_transaction_binned = NULL
fullDataDF$Starting_Instalment_binned_kmeans = NULL
fullDataDF$Starting_Instalment_binned = NULL
fullDataDF$Maturity_Period_binned_kmeans = NULL
fullDataDF$Maturity_Period_binned = NULL
fullDataDF$Starting_outstanding_binned_kmeans = NULL
fullDataDF$Starting_outstanding_binned = NULL
fullDataDF$Starting_Loan_to_Appraisedvalu_Percent_binned_kmeans = NULL
fullDataDF$Starting_Loan_to_Appraisedvalu_Percent_binned = NULL
fullDataDF$StartingInterestrate_binned_kmeans = NULL
fullDataDF$StartingInterestrate_binned = NULL
fullDataDF$RealEstate_Starting_Inflation_binned_kmeans = NULL
fullDataDF$RealEstate_Starting_Inflation_binned = NULL
fullDataDF$Current_Instalment_Sequence_binned_kmeans = NULL
fullDataDF$Current_Instalment_Sequence_binned = NULL
fullDataDF$Current_Outstanding_binned_kmeans = NULL
fullDataDF$Current_Outstanding_binned = NULL
fullDataDF$Current_Loan_to_Appraisedvalu_Percent_binned_kmeans = NULL
fullDataDF$Current_Loan_to_Appraisedvalu_Percent_binned = NULL
fullDataDF$RealEstate_Current_Inflation_binned_kmeans = NULL
fullDataDF$RealEstate_Current_Inflation_binned = NULL
fullDataDF$Remaining_loan_tenure_binned_kmeans = NULL
fullDataDF$Remaining_loan_tenure_binned = NULL
fullDataDF$loan_paid_off_binned_kmeans = NULL
fullDataDF$loan_paid_off_binned = NULL
fullDataDF$CurrentInterestrate_binned_kmeans = NULL
fullDataDF$CurrentInterestrate_binned = NULL
fullDataDF$GDP_binned_kmeans = NULL
fullDataDF$GDP_binned = NULL
fullDataDF$UnemploymentRate_binned_kmeans = NULL
fullDataDF$UnemploymentRate_binned = NULL

```

* Identify the categorical and numerical attributes appropriately

```{r}
cat_Attr = c("ProfessionalLicensure","eCommerceAccount","SocialMediaAccount",
             "NoOfProperties","Asset_type","Urban_Development","Villa_House",
             "Investment_SelfOccupied","Payment_Status")
# print("Caterorical Attributes: ")
# print(cat_Attr)

```

```{r}
num_Attr = setdiff(colnames(fullDataDF), cat_Attr)

# print("Numerical Attributes: ")
# print(num_Attr)
```

*Converting the class of all the categorical features to factor

```{r}
fullDataDF[cat_Attr] <- lapply(fullDataDF[cat_Attr], factor)
```

* Convert the CustomerID of the dataset to the row names which will later help in visualising the clusters

```{r}
rownames(fullDataDF) <- fullDataDF$CustomerID

```

* Dropping CustomerID column as the information is already captured as row names

```{r}
fullDataDF$CustomerID = NULL
```

* There are no missing values in the dataset

```{r}
# Make a copy of the dataframe for later use (mixed attributes)
fullDataDF_ori = fullDataDF
```
 
* Converting categorical features to numeric features by using dummy
_ ProfessionalLicensure _

```{r}
library("dummies")
ProfessionalLicensure_Dummies = data.frame(dummy(fullDataDF$ProfessionalLicensure))
# name the new attributes appropriately
names(ProfessionalLicensure_Dummies) = c("ProfessionalLicensure0","ProfessionalLicensure1")
# head(ProfessionalLicensure_Dummies)
```

_ eCommerceAccount _

```{r}
eCommerceAccount_Dummies = data.frame(dummy(fullDataDF$eCommerceAccount))
# name the new attributes appropriately
names(eCommerceAccount_Dummies) = c("eCommerceAccount0","eCommerceAccount1")
# head(eCommerceAccount_Dummies)
```

_ SocialMediaAccount _

```{r}
SocialMediaAccount_Dummies = data.frame(dummy(fullDataDF$SocialMediaAccount))
# naming the new attributes appropriately
names(SocialMediaAccount_Dummies) = c("SocialMediaAccount_No","SocialMediaAccount_Yes")
# head(SocialMediaAccount_Dummies)
```

_ NoOfProperties _

```{r}
NoOfProperties_Dummies = data.frame(dummy(fullDataDF$NoOfProperties))
# naming the new attributes appropriately
names(NoOfProperties_Dummies) = c("NoOfProperties_1","NoOfProperties_2", "NoOfProperties_3","NoOfProperties_4")
# head(NoOfProperties_Dummies)
```

__ Asset_type __

```{r}
Asset_type_Dummies = data.frame(dummy(fullDataDF$Asset_type))
# naming the new attributes appropriately
names(Asset_type_Dummies) = c("Asset_type_Complex_With_shared_services", "Asset_type_No_shred_services")
# head(Asset_type_Dummies)
```

__ Urban_Development  __

```{r}
Urban_Development_Dummies = data.frame(dummy(fullDataDF$Urban_Development))
# naming the new attributes appropriately
names(Urban_Development_Dummies) = c("Urban_Development_No","Urban_Development_Yes")
# head(Urban_Development_Dummies)
```

__ Villa_House  __

```{r}
Villa_House_Dummies = data.frame(dummy(fullDataDF$Villa_House))
# naming the new attributes appropriately
names(Villa_House_Dummies) = c("Villa_House_No","Villa_House_Yes")
# head(Villa_House_Dummies)
```

__ Investment_SelfOccupied  __ 

```{r}
Investment_SelfOccupied_Dummies = data.frame(dummy(fullDataDF$Investment_SelfOccupied))
# naming the new attributes appropriately
names(Investment_SelfOccupied_Dummies) = c("Investment_SelfOccupied_Investment", "Investment_SelfOccupied_Self_Occupancy")
# head(Investment_SelfOccupied_Dummies)
```

__ Payment_Status  __ 

```{r}
Payment_Status_Dummies = data.frame(dummy(fullDataDF$Payment_Status))
# naming the new attributes appropriately
names(Payment_Status_Dummies) = c("Payment_Status_Default", "Payment_Status_Non-Payoff/Non-Default", "Payment_Status_Payoff")
# head(Payment_Status_Dummies)
```

* Removing the original categorical features and adding the newly created dummy features

```{r}
fullDataDF$ProfessionalLicensure = NULL
fullDataDF$eCommerceAccount = NULL
fullDataDF$SocialMediaAccount = NULL
fullDataDF$NoOfProperties = NULL
fullDataDF$Asset_type = NULL
fullDataDF$Urban_Development = NULL
fullDataDF$Villa_House = NULL
fullDataDF$Investment_SelfOccupied = NULL
fullDataDF$Payment_Status = NULL


fullDataDF = data.frame(cbind(fullDataDF, ProfessionalLicensure_Dummies, eCommerceAccount_Dummies, SocialMediaAccount_Dummies, NoOfProperties_Dummies, Asset_type_Dummies, Urban_Development_Dummies, Villa_House_Dummies, Investment_SelfOccupied_Dummies, Payment_Status_Dummies))
```

* The data must be scaled, before measuring any type of distance metric as the variables with higher ranges will significantly influence the distance

```{r}
num_Attr <- num_Attr[ num_Attr != "CustomerID" ]
# num_Attr
```

```{r}
fullDataDF[, num_Attr] =  scale(fullDataDF[,num_Attr], center = T, scale = T)
``` 

* Saving a CSV file of fullDataDF 

```{r}
#Saving a CSV file of fullDataDF  
rownames(fullDataDF) -> fullDataDF$CustomerID
write.csv(fullDataDF, "fullDataDF_preprocessed2.csv", row.names=F)
```


