---
title: "Untitled"
author: "Sanjyot Godbole"
date: "May 16, 2019"
output: 
  html_document:
    toc: true
    theme: united
    toc_depth: 4
    toc_float:
      collapsed: false
      smooth_scroll: false  
---

```{r}
# clear your environment
rm(list = ls(all=TRUE))
```


# Reading & Understanding the Data

* Make sure the dataset is located in your current working directory

```{r}
input_data = read.csv('trainDF_for_Clustering_18-12-01.csv', header = T)
```


* Use the str(), summary() functions to get a feel for the dataset.

```{r}
str(input_data)
```

```{r}
summary(input_data)
```


# Data Pre-processing


* Attribute 'ProfessionalLicensure', 'eCommerceAccount' and 'NoOfProperties' are categorical variables. Lets convert appropriately.

```{r}
input_data$ProfessionalLicensure = as.factor(as.character(input_data$ProfessionalLicensure))

input_data$eCommerceAccount = as.factor(as.character(input_data$eCommerceAccount))
input_data$NoOfProperties = as.factor(as.character(input_data$NoOfProperties))

#Now see the structure of the dataframe
str(input_data)
```

## Identify the categorical and numerical attributes appropriately

```{r}

# extract the names of categorical columns
categorical_cols = c()

for (coln in names(input_data)){
  if (is.factor(input_data[[coln]])){
    categorical_cols = append(categorical_cols,coln)
  }
}

categorical_cols = setdiff(categorical_cols,"CustomerID")
print(categorical_cols)
```

```{r}
#Now, how to find the numerical attributes?
numerical_cols = setdiff(colnames(input_data), categorical_cols)

numerical_cols = setdiff(numerical_cols,"CustomerID")
numerical_cols
```


* Convert the Customer IDs to the row names, as this will later help us in visualising the clusters

```{r}
rownames(input_data) <- input_data$CustomerID
customerID = input_data$CustomerID

```

## Drop the CustomerID column 
* (As it is now just redundant information)

```{r}
input_data$CustomerID = NULL
# OR
# input_data <- input_data[, -c(colnames(input_data) %in% ("name"))]
```


* Find the number of missing values and either impute or omit them

```{r}
sum(is.na(input_data))
```

* There are no missing values in dataset

```{r}
# check no missing value in categorical column
# sum(is.na(input_data$shelf))
# had there been any missing value we would have imputed it seperately from numerical using modes.
```

# Multiple Linear Regression

```{r}
model = lm(CreditRiskScore~.,input_data)
summary(model)
```


```{r}
plot(model)
```

# Variance Inflation Factor

```{r}
library(car)
vif(model)
```

# StepAIC

```{r}
library(MASS)

#Stepwise Regression
inputData_step <- stepAIC(lm(CreditRiskScore~.,input_data), direction="both")
```

# Multiple Linear Regression after feature selection by stepAIC

```{r}
model2 = lm(CreditRiskScore ~ eCommerceAccount + age_in_years + Total_no_of_loan_tenure_with_current + 
    Villa_House + Investment_SelfOccupied + Payment_Status + 
    Remaining_loan_tenure + ratio_RE_inflation + ratio_Loan_to_Appraisedvalu_Percent + 
    ratio_Interestrate + ratio_outstanding + diff_Salary_Utility + 
    ratio_curr_outstanding_Salary,input_data)
summary(model2)



```

```{r}
class(model2)

```
# Feature Importance

```{r}
library(caret)
FeatureImp =  varImp(model2)
FeatureImp$Feature = rownames(FeatureImp)

names(FeatureImp) = c("Importance", "Feature")
FeatureImp = FeatureImp[order(-FeatureImp$Importance),]


library(ggplot2)

p = ggplot(FeatureImp, aes(x = reorder(Feature, Importance), y = Importance, fill = Importance)) + geom_col() + coord_flip()

p
```